
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{hyperref}

\title{The Parasite Machine: A Minimal Relational Logic}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Abstract}
We define a minimal machine---the \emph{Parasite}---that operates on relations rather than substances.
It consists of a directed relation $A \rightarrow B$ and a third position $C$ that acts on the relation itself.
The third position can operate as noise or as a metastable entity.
Roles $(A,B,C)$ are not intrinsic and may permute.
A distance parameter controls the strength of $C$'s action.
We show how this machine generates structure without conserved quantities or predefined ontology.

\section*{1. Primitive structure}
We begin with a directed relation:
\[
A \rightarrow B
\]
and a third position $C$ that acts on the relation:
\[
C \triangleright (A \rightarrow B).
\]
No assumption is made that $A,B,C$ are substances.
They are positions within a relational configuration.

\section*{2. Distance and coupling}
Let $d \ge 0$ denote the distance of $C$ to the relation.
Define coupling:
\[
k = \frac{1}{d + \epsilon}.
\]
As $d \to \infty$, $k \to 0$ (negligible influence).
As $d \to 0$, $k \to \infty$ (dominant influence).

\section*{3. Noise and metastability}
The third position $C$ operates in two regimes:
\begin{itemize}[leftmargin=2em]
\item \textbf{Noise}: perturbative, destabilizing.
\item \textbf{Metastability}: stabilized, structuring.
\end{itemize}
These are not distinct ontologies but regimes of the same position.

\section*{4. Transformation of relations}
Let $R(A,B)$ denote the baseline relation strength.
Define a transformation:
\[
R'(A,B) = T(R(A,B), C, k).
\]
Two cases:
\begin{align*}
\text{Noise: } & R' = R + \eta(C)\,k \\
\text{Metastability: } & R' = R + \alpha \, C \, k
\end{align*}
where $\eta$ is a stochastic perturbation and $\alpha$ a scaling constant.

\section*{5. Role permutation}
Positions are not fixed. Let $\sigma$ be a permutation:
\[
(A,B,C) \mapsto \sigma(A,B,C).
\]
This encodes sudden reassignment of roles.

\section*{6. Iteration}
The machine evolves by iteration:
\begin{enumerate}[leftmargin=2em]
\item compute transformed relation $R'$
\item update positions $(A,B,C)$
\item possibly permute roles
\item possibly adjust distance $d$
\end{enumerate}
Formally:
\[
(A,B,C)_{t+1} = \Phi(A,B,C,d).
\]

\section*{7. Emergence}
Without assuming:
\begin{itemize}[leftmargin=2em]
\item conserved quantities,
\item substances,
\end{itemize}
the system produces:
\begin{itemize}[leftmargin=2em]
\item stable regimes,
\item clusters,
\item metastable entities,
\item shifting relations.
\end{itemize}

\section*{8. Interpretation}
The Parasite machine demonstrates:
\begin{itemize}[leftmargin=2em]
\item structure emerges from relational transformation,
\item noise and entity are phase regimes,
\item roles are positional, not intrinsic,
\item ontology is not presupposed but produced.
\end{itemize}

\section*{9. Final statement}
A system of relations, perturbed and stabilized by a third term, can generate entities and structure without recourse to conserved substance or fixed ontology.

\end{document}
