
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{hyperref}

\title{The Parasite Machine:\\
A Unified Framework Across Logic, Geometry, and Computation}
\author{}
\date{}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}

\begin{document}
\maketitle

\section*{Abstract}
We consolidate the Parasite framework into a unified system spanning:
\begin{itemize}
\item asymmetric dynamical relations,
\item tetralemmatic logical regimes,
\item conic geometric structures,
\item and computational instantiation.
\end{itemize}

\section{1. Narrative Motivation}
We begin from a rejection:
\begin{itemize}
\item no substances,
\item no conserved quantities,
\item no fixed ontology.
\end{itemize}

Instead we assume only:
\begin{itemize}
\item positions,
\item relations,
\item transformations,
\item observables.
\end{itemize}

\paragraph{Narrative}
The goal is not to describe a world, but to generate one.

\section{2. Asymmetric Relation}

\begin{definition}
\[
R(A,B) = (\iota_{AB}, \delta_{AB})
\]
\end{definition}

\paragraph{Narrative}
Relations are primitive, directional, and intensive.

\section{3. Implied Counter-Relation}

\begin{definition}
\[
\Phi_m : R(A,B) \mapsto R(B,A)
\]
\end{definition}

\paragraph{Narrative}
Reciprocity is not assumed; it is generated.

\section{4. Representation as Geometry}

\[
\mathcal{M} = \{Id, Res, An, Con\}
\]

\[
\kappa(m) \in \{ellipse, parabola, hyperbola, mixed\}
\]

\paragraph{Narrative}
Representation is curvature, not correspondence.

\section{5. Parasite Operator}

\begin{definition}
\[
C \triangleright_m (A \rightarrow B)
\]
\end{definition}

\paragraph{Narrative}
The third term acts on the relation itself.

\section{6. Tetralemma}

\[
\tau(R) \in \{affirmed, negated, both, neither\}
\]

\paragraph{Narrative}
Logical states become dynamical regimes.

\section{7. Full Machine}

\begin{definition}
\[
P = (A,B,C,R,\Phi,m,\tau,d)
\]
\end{definition}

\[
P' = \Psi(P)
\]

\paragraph{Narrative}
Everything evolves.

\section{8. Computational Instantiation}

The Parasite machine is implemented as a dynamical system:
\begin{itemize}
\item asymmetric relations updated per step,
\item implied counter-relations generated via mode,
\item tetralemma evaluated,
\item parasite perturbs system,
\item roles permuted.
\end{itemize}

\paragraph{Narrative}
The code is not an example. It is a proof of concept.

\section{9. Conceptual Synthesis}

\begin{itemize}
\item asymmetry is primitive
\item reciprocity is derived
\item representation is curvature
\item logic is phase space
\item the parasite is mediation
\end{itemize}

\section*{Final Statement}

A world emerges from relations, their implied returns, and a third term that modulates their curvature.

\end{document}
